**The Place of Interoception and Theory of Mind in Deception**

### 2021-12-07 1_Measures.Rmd
move data merging to data processing file
HTT (originally in measures) and physio (original in python)

```{r message=FALSE}
htt_data <- read.csv("scripts/claudia/HCT_Tracking.csv") |> 
  mutate(Participant = paste0("S", as.character(ID)),
         Condition = fct_recode(Condition, "NoGuessPerturbed" = "NoGuess_Perturbed")) |> 
  rename(Distance = Time_to_Rpeak)

htt_data |>
  ggplot(aes(x = Distance, fill = Condition)) +
  geom_histogram(binwidth = 0.05, alpha = 0.5, position="identity") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_wrap(~ID) +
  see::theme_modern()

# model <- rstanarm::stan_lmer(Distance ~ Condition + (1 + Condition | ID), data = hct_data, refresh=0, chains = 2)
# model <- glmmTMB::glmmTMB(Distance ~ Condition + (1 | ID), data = hct_data)

htt_scores <- htt_data |> 
  group_by(Participant, Condition) |> 
  summarise(HTT_Mean = mean(Distance),
            HTT_n = n()) |> 
  ungroup() |> 
  complete(Participant, Condition, fill = list(HTT_Mean = NA, HTT_n = 0)) |> 
  tidyr::pivot_wider(names_from = "Condition", values_from = c("HTT_Mean", "HTT_n"))

df <- merge(df, htt_scores, by = "Participant")
```

>>>>

```{r message=FALSE}
htt_data <- read.csv("preprocessing/HTT_extracted.csv") |> 
  mutate(Condition = fct_recode(Condition, "NoGuessPerturbed" = "NoGuess_Perturbed")) |> 
  rename(Distance = Time_to_Rpeak)

htt_data |>
  ggplot(aes(x = Distance, fill = Condition)) +
  geom_histogram(binwidth = 0.05, alpha = 0.5, position="identity") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_wrap(~ID) +
  see::theme_modern() 
```

### 2021-12-07 index.Rmd
move data merging to data processing file
HTT (originally in measures) and physio (original in python)

```{r warning=FALSE, message=TRUE, results='asis'}
# setwd("C:/Users/user/Desktop/Sputnik/2019-23/DeceptionInteroTom")

df <- read.csv("data/data_combined_wPhysio.csv") %>% 
  mutate(ID = as.factor(paste0("S", ID)),
         Condition = as.factor(Condition),
         Item = as.factor(Item),
         Phrasing = as.factor(Phrasing),
         Answer = as.factor(Answer)) |> 
  rename("HeartRate" = "ECG_Rate_MeanRaw_1.5_2.5s") |> 
  dplyr::filter(!Participant %in% c("S3", "S15", "S19", "S23"))  # No data

>>>>

```{r warning=FALSE, message=TRUE, results='asis'}
df <- read.csv("data/data_combined.csv") %>% 
  mutate(Participant = as.factor(paste0("S", Participant)),
         Condition = as.factor(Condition),
         Item = as.factor(Item),
         Phrasing = as.factor(Phrasing),
         Answer = as.factor(Answer)) |> 
  dplyr::filter(!Participant %in% c("S3", "S15", "S19", "S23"))  # No data

### 2021-12-07 preprocessing/data processing.Rmd
move data merging to data processing file
HTT (originally in measures) and physio (original in python)

@@

mydata <- data.frame()
for (participant in list.files("../data/data_experimental")) {
  df_sub <- read.csv(paste0("../data/data_experimental/", participant, "/deception/", participant, "_deceptiontask.csv"), header = FALSE)[-c(1:11), c(1:4, 29, 31, 35, 36, 43, 45, 47)] %>% 
    mutate(Trial = c(1:80),
           Condition = c(rep("Social", 40), rep("Polygraph", 40)))
  mydata <- rbind(mydata, df_sub)
}

@@

  mutate(Confidence = as.numeric(Confidence),
         social_start = as.numeric(social_start),
         social_stop = as.numeric(social_stop),
         polyg_start = as.numeric(polyg_start),
         polyg_stop = as.numeric(polyg_stop),
         ID = as.numeric(ID)) %>%
  mutate(RT = ifelse(Condition == "Social", social_stop - social_start,
         ifelse(Condition == "Polygraph", polyg_stop - polyg_start, NA))) %>%

  select(ID, Trial, Condition, everything()) # move columns to front

@@

```{r combine data}
qn <- paste0("Q", 1:40)
data_combined <- read.csv("deceptiontask_extracted.csv") %>% 
  select(-c(contains("start")|contains("stop"))) %>% 
  left_join(read.csv("yoni_processed.csv")) %>% 
  left_join(read.csv("BES_processed.csv")) %>% 
  select(-c(contains(paste0("Q", 0:9)))) %>%
  left_join(read.csv("HCT_processed.csv")) %>% 
  left_join(read.csv("MAIA2_processed.csv")) %>% 
  select(-c(contains(paste0("Q", 0:9)))) %>%
  left_join(read.csv("lie_processed.csv")) %>% 
  select(-c(contains(paste0("Q", 0:9)))) %>%
  left_join(read.csv("demo.csv")) %>% 
  select(-c(Name, Matric, HP, Email, Birthday, School, Course, LivedinSG)) %>% 
  rename(Participant = ID) %>% 
  mutate(Answer = fct_recode(Answer, Lie = "LIE", Truth = "TRUTH"))

>>>>

```{r int obj htt}
rm(list=ls())
cat("\014")

mydata <- read.csv("HTT_extracted.csv") %>% 
  mutate(Condition = fct_recode(Condition, "NoGuessPerturbed" = "NoGuess_Perturbed")) %>% 
  rename(Distance = Time_to_Rpeak)

results <- mydata %>% 
  group_by(ID, Condition) %>% 
  summarise(HTT_Mean = mean(Distance),
            HTT_n = n()) %>%  
  ungroup() %>% 
  complete(ID, Condition, fill = list(HTT_Mean = NA, HTT_n = 0)) %>% 
  tidyr::pivot_wider(names_from = "Condition", values_from = c("HTT_Mean", "HTT_n"))

write.csv(results, file = "HTT_processed.csv", row.names=FALSE)
```

@@

mydata <- data.frame()
for (participant in list.files("../data/data_experimental")) {
  df_sub <- read.csv(paste0("../data/data_experimental/", participant, "/deception/", participant, "_deceptiontask.csv"), header = FALSE)[-c(1:11), c(1:4, 29, 31, 35, 36, 43, 45, 47)] %>% 
    mutate(trial = c(1:80),
           condition = c(rep("Social", 40), rep("Polygraph", 40)))
  mydata <- rbind(mydata, df_sub)
}

@@

  mutate(Confidence = as.numeric(Confidence),
         social_start = as.numeric(social_start),
         social_stop = as.numeric(social_stop),
         polyg_start = as.numeric(polyg_start),
         polyg_stop = as.numeric(polyg_stop),
         ID = as.numeric(ID)) %>%
  mutate(RT = ifelse(condition == "Social", social_stop - social_start,
         ifelse(condition == "Polygraph", polyg_stop - polyg_start, NA))) %>%

  select(ID, trial, condition, everything()) # move columns to front

@@

```{r combine data}
qn <- paste0("Q", 1:40)
data_combined <- read.csv("deceptiontask_extracted.csv") %>% 
  select(-c(contains("start")|contains("stop"))) %>% 
  left_join(read.csv("deceptiontask_physio_processed.csv")) %>% 
  left_join(read.csv("yoni_processed.csv")) %>% 
  left_join(read.csv("BES_processed.csv")) %>% 
  select(-c(contains(paste0("Q", 0:9)))) %>%
  left_join(read.csv("HCT_processed.csv")) %>% 
  left_join(read.csv("HTT_processed.csv")) %>% 
  left_join(read.csv("MAIA2_processed.csv")) %>% 
  select(-c(contains(paste0("Q", 0:9)))) %>%
  left_join(read.csv("lie_processed.csv")) %>% 
  select(-c(contains(paste0("Q", 0:9)))) %>%
  left_join(read.csv("demo.csv")) %>% 
  select(-c(Name, Matric, HP, Email, Birthday, School, Course, LivedinSG)) %>% 
  rename(Participant = ID,
         Trial = trial,
         Condition = condition,
         HeartRate = ECG_Rate_MeanRaw_1.5_2.5s) %>%
  mutate(Answer = fct_recode(Answer, Lie = "LIE", Truth = "TRUTH"))
